%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
% sRun --> latexmk -xelatex "CV.tex" -pvc -f --> R always
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{setspace}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-14pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-8pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-0.5pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-0.5pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-0.5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-2pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\setstretch{1.0}
\footnotesize{
% \vspace{10mm}
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Arnau Puche}} & Email : \href{mailto:arnaupuchevila@gmail.com}{arnaupuchevila@gmail.com}\\
  \href{https://github.com/puchee99}{https://github.com/puchee99} & Mobile : (+34)-673-821-695 \\
\end{tabular*}
% %-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart 
  \resumeSubheading
      {Universitat Autònoma de Barcelona}{Bellaterra, Spain}
      {Bachelor's degree of Data Engineering (240 ECTS);  Avg. Grade: 7.13}{Sep. 2018 -- Present}
      \begin{itemize}
        \item{\textbf{TFG:} market analysis using AI algorithms to identify patterns and trends that optimize financial decision-making.}
        \end{itemize}
  \resumeSubheading
      {Coursera}{}
      {Data Science}{Sep. 2020 -- Present}
      \begin{itemize}
      \item{\textbf{IBM AI Entreprise Workflow:} connecting business priorities to technical implementations.}
      \item{\textbf{Neural Networks and Deep Learning:} foundational concept by Andrew Ng.}
      \item{\textbf{Fraud Detection on Financial Transactions with ML on GCP:} BigQuery and VertexAI for banking industry.}
      \end{itemize}

  \resumeSubheading
      {DeepLearning.AI}{}
      {Data Science}{April. 2023 -- Present}
      \begin{itemize}
      \item{\textbf{ChatGPT Prompt Engineering for Developers:} how to use a large language model (LLM) to quickly build new and powerful applications.}
      \end{itemize}

  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
          {CaixaBank Tech}{Barcelona, Spain}
          {Data Scientist - ML Engineer}{August 2022 - July 2023}

          \textbf{Tools:} Python, SQL, Bash, Elastic, Gitlab, 
          \begin{itemize}
          \item{\textbf{Anomaly Detection:} Detect anomalies in the failures of the entire infrastructure through different AI models.}
          \item{\textbf{Clustering:} categorize errors using advanced clustering techniques to obtain more information.}
          \item{\textbf{Forecasting:} prediction of different KPI.}
          \item{\textbf{ElasticSearch:} create and modify indexes.}
          \item{\textbf{XAI:} express why an AI system reached a particular decision, recommendation, or prediction.}
          \item{\textbf{ML Engineer:} design self-running software to automate predictive models.}
    \end{itemize}

    \resumeSubheading
          {UAB}{Bellaterra, Spain}
          {Research Assistant}{Sept 2021 - Feb 2022}
          \textbf{Tools:} Python, SQL, Bash
          \begin{itemize}
          \item{\textbf{Database:} Create a SQL database from biomedical device data.}
          
          \end{itemize}
    \resumeSubheading
      {UVE Solutions}{Manresa, Spain}
      {Intern Data Scientist}{Feb 2021 - July 2021}
     
      \textbf{Tools:} Python, SQL, Bash, Streamlit, Pandas, Bitbucket, Confluence, Jira
      \begin{itemize}
      \item{\textbf{Data ingestion:} Build a data ingestion tool (Streamlit App) to perform ETL on different data formats. ML techniques were used to calculate similarity between words.}
      \item{\textbf{BI:} Analyze the distribution of the hostelry sector in the Spanish territory.
      }
      
      \end{itemize}
      
  \resumeSubHeadingListEnd

  %-----------FreeLance-----------------
\section{Freelance}
\resumeSubHeadingListStart
    \resumeSubheading
          {KeepUp Talent}{Barcelona, Spain}
          {Data Scientist - ML Engineer}{April 2022 - July 2023}

          \textbf{Tools:} Python, SQL, Bash, PowerBI, Sharepoint, Microsoft Forms
          \begin{itemize}
          \item{\textbf{App Infrastructure:} create a Microsoft Form to consult small and medium-sized companies.}
          \item{\textbf{Business Reports:} show most relevant insight and how to improve in a PowerBI Dashboard.}
    \end{itemize}
      
  \resumeSubHeadingListEnd

% %-----------HACKATHONS-----------------
  \section{Hackathons}
  \resumeSubHeadingListStart
      \resumeSubheading
          {NUWE JOBarcelona 2022 Final (7 h)}{Camp Nou, Barcelona, Spain}
          {Data (teams of 4) - 1st}{May 2022}
          \textbf{Tools:} Python, Github \href{https://github.com/puchee99/Final-JOBarcelona-22}{\textbf{(Repo link)}}, Bash, Pytorch, Sckiit-Learn, Streamlit, Pandas, XGBoost
          
          \textbf{Challenge:}{ Predict the fair market value of football players.}
          \begin{itemize}
            \item{\textbf{Feature Engineering:} Through different techniques and combinations with the columns, we were able to add new variables with a higher correlation.}
            \end{itemize}
          \begin{itemize}
          \item{\textbf{Multivariant Regression:} We use different ML models with Grid Search to find the best parameters. We also tested with neural networks.}
          \end{itemize}

      \resumeSubheading
        {NUWE CaixaBank 2022 (14 h)}{online}
        {Data - }{May 2022}
        \textbf{Tools:} Python, Github \href{https://github.com/puchee99/CaixaBank_DS}{\textbf{(Repo link)}} , Bash, Pytorch, Sckiit-Learn, Pandas, XGBoost

        \textbf{Challenge:}{ Modeling a predictive algorithm that allows knowing the future dynamics of the market from the historical data of the value of the IBEX35 and some Tweets.}
  
        \begin{itemize}
          \item{\textbf{Sentiment analysis:} Some new columns were added in the market data. One was made by tweet's daily sentiment score. Other columns with popularity information from Google Trends.}      
        \end{itemize}
        \begin{itemize}
        \item{\textbf{Time Series Forecasting:} Tested different Time Series and Classification models (up - down) .
        }      
        \end{itemize}
      \resumeSubheading
        {NUWE Talent Squad 2022 (1 week)}{online}
        {Data - 1st}{July 2022}
        \textbf{Tools:} Python, Github \href{https://github.com/puchee99/TalentSquad22}{\textbf{(Repo link)}} , Bash, Pytorch, Sckiit-Learn, Pandas
        
        \textbf{Challenge:}{ The dataset was data created by sensors from the company SpaceX. The goal was to classify the data into 5 types of weather conditions in order to manage the flight.}
        \begin{itemize}
        \item{\textbf{Multivariant Classification:} Neural networks were used.
      \end{itemize}

      \resumeSubheading
        {NUWE JOBarcelona 2022 Classification (1 week)}{online}
        {Data - Qualified for the final}{April 2022}
        \textbf{Tools:} Python, Github \href{https://github.com/puchee99/JOBcn-DS-2022}{\textbf{(Repo link)}} , Bash, Pytorch, Sckiit-Learn, Pandas
        
        \textbf{Challenge:}{ Classify insects according to the value of different sensors.}
        \begin{itemize}
        \item{\textbf{Multivariant Classification:} Neural networks were used.
      \end{itemize}
        
        
    \resumeSubHeadingListEnd


% %-----------PROJECTS----------------- https://github.com/puchee99/we-CAN 
% \section{Projects}
% \resumeSubHeadingListStart
% \resumeSubheading
%       \item{\textbf{Tools:} Python, SQL, Bash}
%       \item{\textbf{Challenge:}{ \href{https://github.com/puchee99/JOBcn-DS-2022}{\textbf{collect, save, clean and analyze} data to make good investments.} 
%       }

% \resumeItemListEnd

% %--------PROGRAMMING SKILLS------------
\section{Projects}
 \resumeSubHeadingListStart
    \item{\textbf{Flask App}{: create a functional app with different databases in the cloud. \href{https://github.com/puchee99/Flask-App}{(Github link)} }
    }
    %\item{\textbf{Airflow}{: test functionalities to collect economic data. \href{https://github.com/puchee99/META-AIRFLOW}{(Github link)} }
    %}
 \resumeSubHeadingListEnd

\section{Programming Skills}
 \resumeSubHeadingListStart
    \item{\textbf{Languages}{:  Python, Javascript, HTML, SQL, R, Bash, C, Scala}
    }
    \item{\textbf{Technologies}{: GCP, Docker, Tableau, AWS, Airflow, MongoDB, Spark, Microsoft tools}
    }
    \item{\textbf{Libraries}{: Pandas, Numpy, Flask, PySpark, Pytorch, Tensorflow, Plotly, Scikit Learn, Streamlit, Shap, Matplotlib, Request, Pymongo, Logging}
    }
 \resumeSubHeadingListEnd



% %-----------LANGUAGES-----------------
\section{LANGUAGES}
    \textbf{Catalan:}{ Native}\hspace{22mm}
    \textbf{Spanish:}{ Native}\hspace{22mm}
    \textbf{English:}{ Professional (B2 Certificate)}

}
\vspace{5mm}

% \scriptsize{CV compiled on {\today} for an X role at Google}


%-------------------------------------------
\end{document}